Quantifying unmet ICU beds in tertiary hospitals in urban India using Prospective Score Matching 

### 2022-09-16 manuscript.Rmd
tabellerna, basdatan,

<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->
Trauma/Injury is a substantial global health problem that disproportionately affects low and middle-income countries (LMIC), resulting in significant mortality and morbidity@traumaLMIC. The annual mortality from injury in India amount to one million casualties @onemilliondead. Health care professionals in many LMIC testify that their medical assessment oftentimes is that a trauma patient should be admitted to the ICU, but aren’t because such resources are scarce, overloaded and unavailable. Their medical judgement is that the lives of these patients were salvageable, and that these patients died as a direct result of not being admitted to the ICU@stuffLMICdoctorssay.

@@

Trauma disproportionately affects young, otherwise healthy individuals. They are often the primary breadwinners for their families and therefore the detrimental impact of trauma go beyond mortality or substantial loss of disease-free years of life for the affected individuals, it also has a considerable financial and social harm on their family members and communities. @traumaLMIC

@@

The theory being examined in this thesis is that there exist subset of the TITCO1 dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the IC for lack of such resources. These patients will be identified using propensity score matching. 
The size of this group in relation to the group that were admitted to the ICU indicate the magnitude of the unmet need of ICU beds. If, for every patient that did receive ICU care, there was another patient with similar predictors that wasn’t admitted due to scarcity of ICU resources, that would mean the ICU resources are 50% of what they ought to be.

@@

<!-- Cohort study: Give the eligibility criteria, and the sources and
methods of selection of participants. Describe methods of
follow-up. For matched studies, give matching criteria and number of
exposed and unexposed -->
The TITCO1 data set includes all data recorded for trauma patients at the participating hospitals. The patients have the common denominators than geographical location and trauma.  
FRÅGA: finns en socioekonomisk selektion ? läs: är detta sjukhus dit vissa socioekonomiska grupper hamnar?

@@

(c) Explain how missing data were addressed 
The data completion rate is presented in table_nums('tab_1'). As the base assumption, all quantitative variables collected for each patient are considered potential recordings. Data that are missing are assumed missing because care for a patient did not motivate the collection of the data. For example, if serum creatinine was not recorded, it is assumed that the collection of this variable wasn't relevant for care of the patient.

>>>>

<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->
Trauma/Injury is a substantial global health problem that disproportionately affects low and middle-income countries (LMIC), resulting in significant mortality and morbidity@traumaLMIC. The annual mortality from injury in India amount to one million casualties @onemilliondead. Half of trauma mortality in India occur in-hospital, and in-hospital trauma mortality in Indian hospitals was double that of high-income countries @indiantrauma. Health care professionals in many LMIC testify that their medical assessment oftentimes is that a trauma patient should be admitted to the ICU, but aren’t because such resources are scarce, overloaded and unavailable. Their medical judgement is that the lives of these patients were salvageable, and that these patients died as a direct result of not being admitted to the ICU@stuffLMICdoctorssay. Globally, an estimated two million lives could be saved annually, if the appropriate and timely trauma care provided by hospitals in many high-income countries were available and provided in low to-middle-income countries (LMICs) @livessaved

@@

Trauma disproportionately affects young, otherwise healthy individuals. They are often the primary breadwinners for their families and therefore the detrimental impact of trauma go beyond mortality or substantial loss of disease-free years of life for the affected individuals, it also carries a considerable financial and social harm on their family members and communities. @traumaLMIC

@@

The theory being examined in this thesis is that there exist subset of the TITCO1 dataset that didn't go to the ICU, but are very similar to the patients that did go to the ICU, in the covariates that caused ICU-treated patients to receive this intervention. The thesis is that these patients were not admitted to the IC for lack of such resources. These patients will be identified using propensity score matching.

The size of this group in relation to the group that were admitted to the ICU indicate the magnitude of the unmet need of ICU beds. If, for every patient that did receive ICU care, there was another patient with similar predictors that wasn’t admitted due to scarcity of ICU resources, that would mean the ICU resources are 50% of what they ought to be.

@@

<!-- Cohort study: Give the eligibility criteria, and the sources and
methods of selection of participants. Describe methods of
follow-up. For matched studies, give matching criteria and number of
exposed and unexposed -->
The TITCO1 data set includes all data recorded for trauma patients of the emergency departments at the participating hospitals. Trauma covers injury and with a mechanism of road traffic, railway, fall, burn or assault. 
FRÅGA: finns en socioekonomisk selektion ? läs: är detta sjukhus dit vissa socioekonomiska grupper hamnar?

47 patients were excluded for anonymization purposes, 120 patients were excluded because they were dead on arrival, and further XX pat were excluded because of missing data.

@@

Missing Data
-------------
The data completion rate is presented in table_nums('tab_1'). As the base assumption, all quantitative variables collected for each patient are considered potential recordings. Data that are missing are assumed missing because care for a patient did not motivate the collection of the data. For example, if serum creatinine was not recorded, it is assumed that the collection of this variable wasn't relevant for care of the patient.
